Verifying Demonstrations

### 2020-03-11 paper/tamarin-spec.tex

\section{Specification of the distance-bounding protocol used by \PRIVO in Tamarin}
\label{apdx:tamarin-spec}

The results provided by Tamarin extends to the protocol being modeled 
only up to the accuracy of the specification of protocol rules (and equational theory).
Moreover, Tamarin specifications are not always able to reproduce a protocol precisely.
Consequently, we provide below the full code of our specification and of the various properties we defined, and briefly explain our choices of modelization.

>>>>

\section{Specification in Tamarin}%
\label{apdx:tamarin-spec}

\sonja{Clarification of these explanations needed. Split up some text
  to go into the body of the paper and leave details (or even just the
  code) in the appendix.}
The results provided by Tamarin extends to the protocol being modeled 
only up to the accuracy of the specification of protocol rules (and equational theory).
Moreover, Tamarin specifications are not always able to reproduce a protocol precisely.
Consequently, we provide below the full code of our specification and of the various properties we defined, and briefly explain our choices of modelization.
